Decentralised location verification system

### 2016-03-31 presentation.tex
updating presentation

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Identities: Duplication}
		Identity duplication is unavoidable in a decentralised system.
		\begin{table}[]
			\begin{tabular}{l|l}
				\textbf{ID} & \textbf{Contents}\\\hline
				\dots & \\\hline
				ffa0 & \\\hline
				ffa1 & \\\hline
				ffa2 & $T_{A4}$ \visible<2->{, \textcolor{red}{$T_{C102}$}}\\\hline
				ffa3 & \\\hline
				ffa4 & $T_{B87}$\\\hline
				\dots & \\
			\end{tabular}
		\end{table}
	\end{frame}
\end{document}

>>>>

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Identities: Duplication}
		Identity duplication is unavoidable in a decentralised system.
		\visible<2->{
		\begin{table}[]
			\begin{tabular}{l|l}
				\textbf{ID} & \textbf{Contents}\\\hline
				\dots & \\\hline
				ffa0 & \\\hline
				ffa1 & \\\hline
				ffa2 & $T_{A4}$ \visible<3->{, \textcolor{red}{$T_{C102}$}}\\\hline
				ffa3 & \\\hline
				ffa4 & $T_{B87}$\\\hline
				\dots & \\
			\end{tabular}
		\end{table}
		}
	\end{frame}

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Transactions}
		Transactions are created when two mobile nodes physically meet.
		\begin{itemize}
			\item Ad-hoc bluetooth connection between the nodes.
		\end{itemize}

		\begin{center}
			\resizebox {0.35\columnwidth} {!} {\includegraphics{diagrams/overview-presentation/mobile-node-meet.png}}
		\end{center}
	\end{frame}

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Transactions II}
		\begin{figure}[t]
			\resizebox {\columnwidth} {!} {\input{diagrams/transaction_presentation.tex}}
		\end{figure}
	\end{frame}
\end{document}
